From physical principles to Hamiltonian mechanics

### 2014-06-30 2014ClassicalHamiltonianDerivation/classicalHamiltonianDerivation.tex
Fixing quotes in bibliography

\bibitem{Jaynes} Jaynes, E. T.: "Information theory and statistical mechanics", (1963)
\bibitem{Shannon} Shannon, C. E.: "A mathematical theory of communications", The Bell System Technical Journal, Vol. 27, pp. 379–423, 623–656, (1948)
\bibitem{Gromov} Gromov, M. L.: "Pseudo holomorphic curves in symplectic manifolds". Inventiones Mathematicae 82: 307–347, (1985)
\bibitem{deGosson} de Gosson, M. A.: "The symplectic camel and the uncertainty principle: the tip of an iceberg?", Foundation of Physics 39, pp. 194–214, (2009)
\bibitem{Stewart} Stewart, I.: "The symplectic camel", Nature 329(6134), 17–18 (1987)
\bibitem{Struckmeier} Struckmeier, J.: "Hamiltonian dynamics on the symplectic extended phase space for autonomous and non-autonomous systems", J. Phys. A: Math. Gen 38, 1257-1278, (2005)
\bibitem{Synge} Synge, J. L.: Encyclopedia of Physics Vol 3/1, Springer (1960)
\bibitem{Lanczos} Lanczos, C.: "The variational principles of mechanics", University of Toronto Press (1949)

>>>>

\bibitem{Jaynes} Jaynes, E. T.: ``Information theory and statistical mechanics'', (1963)
\bibitem{Shannon} Shannon, C. E.: ``A mathematical theory of communications'', The Bell System Technical Journal, Vol. 27, pp. 379–423, 623–656, (1948)
\bibitem{Gromov} Gromov, M. L.: ``Pseudo holomorphic curves in symplectic manifolds''. Inventiones Mathematicae 82: 307–347, (1985)
\bibitem{deGosson} de Gosson, M. A.: ``The symplectic camel and the uncertainty principle: the tip of an iceberg?'', Foundation of Physics 39, pp. 194–214, (2009)
\bibitem{Stewart} Stewart, I.: ``The symplectic camel'', Nature 329(6134), 17–18 (1987)
\bibitem{Lanczos} Lanczos, C.: ``The variational principles of mechanics'', University of Toronto Press (1949)
\bibitem{Synge} Synge, J. L.: Encyclopedia of Physics Vol 3/1, Springer (1960)
\bibitem{Struckmeier} Struckmeier, J.: ``Hamiltonian dynamics on the symplectic extended phase space for autonomous and non-autonomous systems'', J. Phys. A: Math. Gen 38, 1257-1278, (2005)
